% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Sam Tanner}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{large}
\begin{letter}{Bently Nevada a Baker Hughes Company.\\
Minden, Nevada 89432}


\begin{flushleft}
{\LARGE\bf Sam dfsdTanner}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill sam.tanner@aggiemail.usu.edu \\
\hfill (801) 941-7217 
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Subject: Application for Internship\\} 
 
\noindent I am highly interested in the intern positions and appreciate the time spent reviewing my application.  Attached is a copy of my resume. I heard of this opportunity through James Decker, another intern from Utah State University.
 

%PARAGRAPH ONE: State reason for letter, name the position or type 
%of work you are applying for and identify source from  which  you 
%learned   of   the  opening.  (i.e.  Career  Development  Center, 
%newspaper, employment service, personal contact). 
 
\noindent 

I am a computer engineering student at Utah State University. I have completed coursework in
Operating Systems, Algorithms and Data Structures, and Electrical and Digital Circuits. I currently work as a lab instructor teaching students to write and debug basic programs on FPGA chips in Verilog. I specialize in C++ and also have experience with Java, Verilog, Flash and CNC. I am learning Perl, and look forward to learning other languages.


%PARAGRAPH  TWO:  Indicate why you are interested in the position, 
%the company, its products, services - above all, stress what  you 
%can  do  for  the employer. If you are a recent graduate, explain 
%how your academic background makes you a qualified candidate  for 
%the  position.  If  you have practical work experience, point out 
%specific achievements or unique qualifications. Try not to repeat 
%the  same  information  the reader will find in the resume. Refer 
%the reader to the enclosed resume or application which summarizes 
%your  qualifications,  training,  and experiences. The purpose of 
%this section is to strengthen your resume  by  providing  details 
%which bring your experiences to life. 
 
\noindent I am particularly interested in working with Micron Technology Inc. because I am passionate about technology and innovation. Micron has done great things with memory and computing in general, and I would be honored to be a part of that.


\noindent I know that I would be an asset to this corporation. I communicate well with others and enjoy working as a member of a team. I absorb material quickly and can put it into practice effectively and efficiently. I am a man of integrity and I aim to exceed expectations.

\noindent I look forward to hearing from you.  I will follow up on this submission in two weeks time via e-mail.  Thank you again for reviewing my application and resume. 




%PARAGRAPH THREE: Request a personal interview and  indicate  your 
%flexibility as to the time and place. Repeat your phone number in 
%the letter and offer assistance to help in a speedy response. For 
%example,  state that you will be in the city where the company is 
%located on a certain date and would like to set up an  interview. 
%Or,  state  that  you  will  call  on a certain date to set up an 
%interview. End the letter by thanking  the  employer  for  taking 
%time to consider your credentials. 
 
\closing{Sincerely,} 
 

 
\encl{Resume}  				% Enclosures

\end{letter}
 \end{large}

\end{document}






